---
output: github_document
---

```{r, echo = FALSE}
version <- as.vector(read.dcf('DESCRIPTION')[, 'Version'])
version <- gsub('-', '.', version)
```

[![R-CMD-check](https://github.com/tsmodels/tsforeign/workflows/R-CMD-check/badge.svg)](https://github.com/tsmodels/tsforeign/actions)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)
[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg?style=flat-square)](commits/master)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/tsforeign)](https://cran.r-project.org/package=tsforeign)


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# tsforeign
Wrappers for part of [**bsts**](https://cran.r-project.org/web/packages/bsts/) package functionality and auto.arima ([**forecast**](https://cran.r-project.org/web/packages/forecast/) package) model to have a common calling convention and common final output (the prediction object). Custom functionality in **bsts** includes predictive decomposition of components and conversion to a [**dlm**](https://cran.r-project.org/web/packages/dlm/) object.

